Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Model

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)
library(modelsummary)

@@

#### Read data ####
analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")

### Model data ####

esg_model <- stan_glm(
  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
  data = analysis_data,
  family = neg_binomial_2(link = "identity"),
  seed = 555
)

modelsummary(esg_model)

>>>>

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)
library(gtsummary)

@@

esg_model <- readRDS(file = here::here("models/esg_model.rds"))

tbl_regression(esg_model)
